### 2016-06-23 README.Rmd

```{r eval=FALSE}
devtools::install_github("cboettig/EML")
```

@@

# An EML document with validation errors
invalid_eml <- system.file("tests/testthat/", "example-eml-invalid.xml", package = "EML")

@@

```{r}
write_eml(eml, "example.xml")
```

@@

>>>>

```{r eval=FALSE}
devtools::install_github("ropensci/EML")
```

@@

# An EML document with validation errors
invalid_eml <- system.file("xsd/test/example-eml-invalid.xml", package = "EML")

@@

```{r, eval=FALSE}
write_eml(eml, "example.xml")
```

@@

### Meta
Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
